\documentclass[12pt]{article}
\input{../app_style.tex}

%%%%%%%%%%%
% App Ex number    %
%%%%%%%%%%%

% DON'T FORGET TO UPDATE

\newcommand{\appno}[1]
{2.4}

%%%%%%%%%%%%%%
% Turn on/off solutions       %
%%%%%%%%%%%%%%

% Off
\newcommand{\soln}[2]{$\:$\\ \vspace{#1}}{}

%%% On
%\newcommand{\soln}[2]{\textit{\textcolor{custom_red}{#2}}}{}

%%%%%%%%%%%%%%%%
% Document
%%%%%%%%%%%%%%%%

\begin{document}
\fontspec[Ligatures=TeX]{Helvetica Neue Light}

Dr. \c{C}etinkaya-Rundel \hfill Sta 101: Data Analysis and Statistical Inference \\
Duke University - Department of Statistical Science \hfill \\

\ttl{Application exercise \appno{}: \\
Normal distribution}

\inst{$\:$ \\
Team name: \rule{10cm}{0.5pt} \\
$\:$ \\
Lab section: $\qquad$ 8:30 $\qquad$ 10:05 $\qquad$ 11:45 $\qquad$ 1:25 $\qquad$ 3:05 \\
$\:$ \\
Write your responses in the spaces provided below. WRITE LEGIBLY and SHOW ALL WORK! 
Only one submission per team is required. One team will be randomly selected and their 
responses will be discussed and graded. Concise and coherent are best!}

Gallup defines engaged employees as those who are involved in, enthusiastic about and committed to their work and workplace. Gallup categorizes workers as engaged based on their responses to key workplace elements it has found to predict important organizational performance outcomes. According to a \href{http://www.gallup.com/poll/181289/majority-employees-not-engaged-despite-gains-2014.aspx?utm_source=EMPLOYEE_ENGAGEMENT&utm_medium=topic&utm_campaign=tiles}{recent Gallup poll}, only 31.5\% of US employees were engaged in their jobs. Suppose that a company employs 1,000 people.

\begin{enumerate}

\item Calculate a range for the plausible number of employees in this sample who are engaged in their jobs. Assume the employees at this company are no different than the average US employee.

\soln{2cm}{
$Binom(n = 1000, p = 0.315)$, $\mu = 1000 \times 0.315 = 315$, $\sigma = \sqrt{1000 \times 0.315 \times 0.685} = 14.7$ \\
Plausible range: $315 \pm 2 \times 14.7 = (285.6, 344.4) \rightarrow$ between 286 to 344 people.
}

\item This company claims that at least 35\% of their employees are engaged. Answer this question using two approaches:

\begin{enumerate}

\item Use the exact binomial probabilities. \textit{Hint:} Computation will be your friend for this part, you \textit{do not} want to do this by hand. Note the code and the answer.

\soln{1cm}{
\texttt{> sum(dbinom(350:1000, size = 1000, prob = 0.315))} \\
\texttt{[1] 0.0098}
}

\item Use the normal approximation to the binomial.

\soln{5cm}{
Success/failure condition: Expected number of successes, $1000 \times 0.315 = 315$, and expected number of
failures, $1000 \times 0.685 = 685$, are both greater than 10; therefore,
\[ Binom(n = 1000, p = 0.315) \sim N(\mu = 315, \sigma = 14.7) \]
\[ P(K > 350) = P\left( Z > \frac{350 - 315}{14.7} \right) = P(Z > 2.38) = 0.0087 \]
}

\end{enumerate}

\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}